Back-integration likelihood

### 2014-01-27 text/notes/likelihood/likelihood.tex
some paper notes

We model the present-day position and velocity of the disrupted star as the result of sampling from isotropic, log-normal distributions centered on the tidal radius, $R_{\rm tide}$, and escape velocity, $V_{\rm esc}$ of the satellite, respectively, at some time $\tau$ in the past, evolved to present day in the parent potential, $\Phi$. In this model, we neglect the effect of self-interaction with the halo of the progenitor [TODO: maybe we need to justify this, add APW's figure from paper 1 ref. response?].

>>>>

We model the present-day position and velocity of the disrupted star as the result of sampling from isotropic, log-normal distributions centered on the tidal radius, $R_{\rm tide}$, and escape velocity, $V_{\rm esc}$, of the satellite, respectively, at some time $\tau$ in the past, evolved to present day in the parent potential, $\Phi$. In this model, we neglect the effect of self-interaction with the halo of the progenitor [TODO: maybe we need to justify this, add APW's figure from paper 1 ref. response?].
